A Partitioning Algorithm for \\ Maximum Common Subgraph Problems

### 2017-08-23 talk/talk.tex
A bold change
Geez a job

\title[A Partitioning Algorithm for Maximum Common Subgraph Problems]{A Partitioning Algorithm for \\
Maximum Common Subgraph Problems}
\author[Ciaran McCreesh, Patrick Prosser and James Trimble]{Ciaran McCreesh, Patrick
Prosser and \\ James Trimble}

@@

\begin{frame}{The Observation Behind our Algorithm}

@@

\begin{frame}[plain,noframenumbering]
    \begin{center}
        \vspace*{4em}
        \url{http://www.dcs.gla.ac.uk/~ciaran} \\
        \vspace{1em}
        \href{mailto:ciaran.mccreesh@glasgow.ac.uk}{\nolinkurl{ciaran.mccreesh@glasgow.ac.uk}} \\
    \end{center}

>>>>

\title[A Partitioning Algorithm for Maximum Common Subgraph Problems]{A Partitioning Algorithm for \\
Maximum Common Subgraph Problems}
\author[Ciaran McCreesh, Patrick Prosser and James Trimble]{\textbf{Ciaran McCreesh}, Patrick
Prosser, and \\ James Trimble}

@@

\begin{frame}{The Observation Behind Our Algorithm}

@@

\begin{frame}[plain,noframenumbering]
    \begin{center}
        \vspace*{4em}
        \url{http://www.dcs.gla.ac.uk/~ciaran} \\
        \vspace{0.2em}
        \href{mailto:ciaran.mccreesh@glasgow.ac.uk}{\nolinkurl{ciaran.mccreesh@glasgow.ac.uk}} \\
        \vspace{2em}
        \textcolor{uofgpillarbox}{
            Are you finding Melbourne to be a bit too warm and dry?  We are hiring a postdoc to work on
            high level constraint modelling for graph problems as part of a ``subgraphs modulo
            theories'' project:} \\
        \vspace{0.2em}
        \href{https://www.vacancies.st-andrews.ac.uk/}{\nolinkurl{https://www.vacancies.st-andrews.ac.uk/}}
        \\ reference AR1972SB
    \end{center}
